A (sun)Shiny Recreation of the New York Times \n Weather Chart

### 2017-04-17 Paper.Rmd
adding notes section, future work bullets

@@

\section{Future Work}

>>>>

```{r, echo = FALSE}
# Notes:
# - Some years there are missing values, they are replacing missing values with 0degreesF; 
#       we will address this in the future work section unless we have time to deal with it before we present
# - Why don't we just start at 1950 since all cities are started by then. Easier then changing where we start for each different city
#
#
#
#
#
```

@@

\section{Future Work}  
  - Fix data inconsistencies 
  - Add in magic turning world
  - Optimizing code
  - Adding in ability to switch to celsius (?)
  - Adding more cities 
  - Add some sort of plotly interactivity/denote record years
